### 2009-11-27 doc/tech_doc/client/client_technical.tex
Updating client technical.

\chapter{Job Description}
\label{sec:jobdesc}

@@

\bibliography{grid, libarcclient}

>>>>

\chapter{Job Description}
\label{sec:jobdesc}
Since new WS-ARC utilizes a middleware plugin structure, it also need to
support the various job description languages used by these middlewares.
Therefore the JSDL, XRSL and JDL job description languages are supported.
In order to provide support for the
three languages listed above, an internal job description data strucuture
is needed which is the union of the supported languages. The internal job
description data structure of new WS-ARC is described in a separate document,
the ARC Job Description Internal Representation~\cite{internaljobdescription}.
%~ Additional
%~ documentation on each of the supported job description languages can be
%~ found in the respective language documentation~\cite{}, but also in the job
%~ description mapping document which documents how the three languages are
%~ mapped in and out from the ARC internal job description data structure~\cite{}.

@@

\bibliography{grid,libarcclient}
